Effective Reionization Likelihood from Planck 2018 Data (?)

### 2021-03-13 paper/rei.tex
Updates from Overleaf

\begin{table}[b]
\centering
\caption{PC chain means $\bar m_a$, standard deviations $\sigma(m_a)$, and correlation matrix $R_{ab}$.}
\label{tab:PC_stats}
\begin{tabular}{|r | r r@{\hskip 0.06in}|r r r r r|}
\hline

@@

@@

The real impact of our range-bound $m_1,m_2$ priors comes from the fact that with the Planck 2018 data, the physicality prior on $m_1$
removes nearly half of the space that would otherwise be allowed by the
data at 95\% CL.  This is in contrast to the Planck 2015 data where only a very small region is removed (see Fig.~\ref{fig:plot_m1m2_2015_vs_2018}).  \wh{Maybe add to the $\tau$ vs $\tau_{12}$ figure a version that does not have this $\tau_{12}$ cut.  Discuss more if the difference significant - also mention that even in the direct tanh constraints, the impact of taking $z\gtrsim 6$ has the effect of removing some of the low $\tau$ region.}.

@@

\begin{figure}[ht]
\includegraphics[width=0.5\textwidth]{paper/plots/pl18_taugtz_pc_zmax30_pl18_srollv2_with_and_without_physicality_prior.pdf}
\caption{$\tau_{12,new}$}
}
\label{fig:tau12}
\end{figure}

>>>>

\begin{table}[b]
\centering
\caption{PC chain means $\bar m_a$, standard deviations $\sigma(m_a)$, and correlation matrix $R_{ab}$. \ch{transpose this table and add a row for taumj, and quote taufid in the caption}}
\label{tab:PC_stats}
\begin{tabular}{|r | r r@{\hskip 0.06in}|r r r r r|}
\hline

@@

\wh{pick a consistent name for this model and use it for the section title, discussion, figure captions and labels - much of the discussion uses ``two step" which would be fine and may be better than high-z}

@@

The real impact of our range-bound $m_1,m_2$ priors comes from the fact that with the Planck 2018 data, the physicality prior on $m_1$
removes nearly half of the space that would otherwise be allowed by the
data at 95\% CL.  This is in contrast to the Planck 2015 data where only a very small region is removed (see Fig.~\ref{fig:plot_m1m2_2015_vs_2018}).  \wh{Maybe add to the $\tau$ vs $\tau_{12}$ figure a version that does not have this $\tau_{12}$ cut.  Mention that even in the direct tanh constraints, the impact of taking $z\gtrsim 6$ also has the effect of removing some of the low $\tau$ region.}

\wh{But it looks like from our conversation (3/12) that this is a small effect on tanh tau with srollv2.  So instead discuss the impact of our priors - mostly it seems to remove negative tau contributions at high $z$ (from looking at the internal Fig 11) and the shifts relative to tanh tau are mostly just the ability to add a small amount of high z ionization that tanh excludes by its form.  Rework this discussion below but I think it is compatible with our conclusion that that our conservative inclusion of some unphysical cases is not biasing our model independent results and instead it is the tanh model that carries a small bias due to its assumed form that excludes the small amount of high-z ionization that is still allowed by the data.}.

@@

\begin{figure}[ht]
\includegraphics[width=0.5\textwidth]{results/tau_pc_decomposition/plot_taumj_decomposition_apply_cut_False_pl18_pc_zmax30_pliklite_srollv2_1015.pdf}
\caption{$\tau_{12,new}$ - \wh{this is an internal plot - leave in for now but also make a version for the paper: just $\tau_{12}$ vs $\tau_{\rm PC}$ in our new convention with and without prior either as a single or separate panel whichever is clearer.}}
\label{fig:tau12}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.5\textwidth]{/paper/plots/plot_tau12_new_apply_cut_False_pl18_pc_zmax30_pliklite_srollv2_1015.pdf}
\caption{$\tau_{12,new}$ (no prior), with prior version is coming}
\label{fig:tau12}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.5\textwidth]{results/tau_pc_decomposition/pl18_taugtz_pc_decomposition_68_only.pdf}
\caption{$\tau$ decomposition (68\% C.L. only) \wh{this is a temporary plot for internal purposes - what I'm seeing here is that without the physicality cut the high $z$ side goes unphysically negative.  I think this is consistent with our description and the $S_1$ curve.}}
\label{fig:tau12}
\end{figure}
